Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-01-16 ms_pre_post.Rmd
Add reference on degeneracy in carnivores, in the context of predator-prey interactions and their effect on prey abundance (Suraci et al. 2017 PLoS One)

Another general inference from our simulation results concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits. The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001]. Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009] and ecosystem [e.g., @Levin2008] dynamics. In the context of reproductive strategy, pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability. Hence, degeneracy occurred in our model through an overlap in how phenotypes cause adaptive inbreeding avoidance. Such degeneracy might increase biological robustness [@Gardner2006; @Whitacre2010a], potentially facilitating realised inbreeding avoidance across environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation). However, evolution of each of these strategies might decrease selection on the other strategy by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression [*sensu* evolution of genetic redundancy; see @Nowak1997]. The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.

@@

|-------|-------------------------------------|-------------|---------------|--------------
| **A** | **Trait**                           | **Allele**  | **Genotype**  | **Phenotype**
|       | Tendency for polyandry              | $P_{a}$     | $P_{g}$       | $P_{p}$
|       | Pre-copulatory inbreeding strategy  | $M_{a}$     | $M_{g}$       | $M_{p}$
|       | Post-copulatory inbreeding strategy | $F_{a}$     | $F_{g}$       | $F_{p}$
|       |                                     |             |               |
| **B** | **Description**                     | **Parameter**  | | **Defaut value(s)**
|       | Cost of tendency for polyandry                 | $c_{P}$        | | $0$, $0.02$
|       | Cost of pre-copulatory inbreeding strategy     | $c_{M}$        | | $0$, $0.02$
|       | Cost of post-copulatory inbreeding strategy    | $c_{F}$        | | $0$, $0.02$
|       | Focal female's number of offspring             | $n$            | | $8$
|       | Log-linear slope of inbreeding depression      | $\beta$        | | $3$
|       | Adult male immigrants per generation           | $\rho$         | | $5$
|       | Female carrying capacity                       | $K_{f}$        | | $100$
|       | Male carrying capacity                         | $K_{m}$        | | $100$
|       | Mutation rate of alleles                       | $\mu$          | | $0.001$
|       | Standard deviation of mutation effect size     | $\mu_{SD}$     | | $\sqrt{1/20}$
|       |                                                |                | |
| **C** | **Description**                                                   | | **Variable** |
|       | Coefficient of kinship                                            | | $k$          |
|       | Focal female's number of mates                                    | | $N_{males}$  |
|       | Female $i$'s perceived absolute mate quality of male $j$          | | $Q^{m}_{ij}$ |
|       | Female $i$'s perceived relative mate quality of male $j$          | | $q^{m}_{ij}$ |
|       | Female $i$'s perceived absolute fertilisation quality of male $j$ | | $Q^{f}_{ij}$ |
|       | Female $i$'s perceived relative fertilisation quality of male $j$ | | $q^{f}_{ij}$ |
|       | Viability of a focal female's offspring                           | | $\Psi_{off}$ |

>>>>

Another general inference from our simulation results concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits. The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001]. Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics. In the context of reproductive strategy, pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability. Hence, degeneracy occurred in our model through an overlap in how phenotypes cause adaptive inbreeding avoidance. Such degeneracy might increase biological robustness [@Gardner2006; @Whitacre2010a], potentially facilitating realised inbreeding avoidance across environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation). However, evolution of each of these strategies might decrease selection on the other strategy by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression [*sensu* evolution of genetic redundancy; see @Nowak1997]. The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.

@@

|       |                                     |             |               |
|-------|-------------------------------------|-------------|---------------|--------------
| **A** | **Trait**                           | **Allele**  | **Genotype**  | **Phenotype**
|       | Tendency for polyandry              | $P_{a}$     | $P_{g}$       | $P_{p}$
|       | Pre-copulatory inbreeding strategy  | $M_{a}$     | $M_{g}$       | $M_{p}$
|       | Post-copulatory inbreeding strategy | $F_{a}$     | $F_{g}$       | $F_{p}$
|       |                                     |             |               |
| **B** | **Description**                     | **Parameter**  |  | **Defaut value(s)**
|       | Cost of tendency for polyandry                 | $c_{P}$        | | $0$, $0.02$
|       | Cost of pre-copulatory inbreeding strategy     | $c_{M}$        | | $0$, $0.02$
|       | Cost of post-copulatory inbreeding strategy    | $c_{F}$        | | $0$, $0.02$
|       | Focal female's number of offspring             | $n$            | | $8$
|       | Log-linear slope of inbreeding depression      | $\beta$        | | $3$
|       | Adult male immigrants per generation           | $\rho$         | | $5$
|       | Female carrying capacity                       | $K_{f}$        | | $100$
|       | Male carrying capacity                         | $K_{m}$        | | $100$
|       | Mutation rate of alleles                       | $\mu$          | | $0.001$
|       | Standard deviation of mutation effect size     | $\mu_{SD}$     | | $\sqrt{1/20}$
|       |                                                |                | |
| **C** | **Description**                                                   | | **Variable** |
|       | Coefficient of kinship                                            | | $k$          |
|       | Focal female's number of mates                                    | | $N_{males}$  |
|       | Female $i$'s perceived absolute mate quality of male $j$          | | $Q^{m}_{ij}$ |
|       | Female $i$'s perceived relative mate quality of male $j$          | | $q^{m}_{ij}$ |
|       | Female $i$'s perceived absolute fertilisation quality of male $j$ | | $Q^{f}_{ij}$ |
|       | Female $i$'s perceived relative fertilisation quality of male $j$ | | $q^{f}_{ij}$ |
|       | Viability of a focal female's offspring                           | | $\Psi_{off}$ |
